

\section*{Executive Summary}	%For left alignment of title
\bigskip
A major concern during disaster search and rescue operations involving large and complex commercial buildings is the process of locating potentially trapped victims. In current conventions, there are no reliable methods of accurately locating trapped victims for first responders, as commercial building structures are large and complex by design. The Akriveia Beacon by TRIWAVE SYSTEMS focuses on creating an safe and dependable solution for indoor location tracking with the objective of locating multiple trapped victims in complex urban environments with pin point accuracy. Such system will allow search and rescue operations to be carried out during small scale disasters such as fires and low magnitude earthquakes safely and efficiently, minimizing potential damages and casualties.

\bigskip
Utilizing various hardware, electrical and software components, the engineers at TRIWAVE SYSTEMS is aiming to create a solution that can accurately and reliably to locate and identify trapped victims within complex structures in near real time. By pinpointing the exact coordinates of any trapped victims associated with an ID tag, the search and rescue time for first responders can be minimized, which is critical in any disaster rescue operations. This is achieved by incorporating a combination of advanced Decawave Ultra-wideband radio frequency (\Gls{RF}) modules, Espressif ESP32 microcontroller units (\Gls{MCU}), data processing units (\Gls{DPU}), and reliable trilateration techniques to create a dependable real time indoor location positioning system.

\bigskip
This project proposal document provides a brief overview of the system architecture; perspective on current markets and potential competitions; discuss project planning; available budget, funding, and cost consideration; as well as an overview of the development team at TRIWAVE SYSTEMS. The proposal will cover the three phases of product development: Proof-of-concept (\Gls{PoC}) phase, Prototype phase, and Final Product phase.

\bigskip
TRIWAVE SYSTEMS is dedicated to creating a reliable and robust indoor location system designed to improve disaster search and rescue operations with human safety as the pivotal focus.
