

\setcounter{section}{3}
\section{References}

\bigskip

\begin{enumerate}[label={[\arabic*]}, leftmargin=*]
\item StatisticsCanada. (2019, May) Fire-related deaths and persons injured, by type of structure. \\
    {[Online]}. Available: https: //www150.statcan.gc.ca/t1/tbl1/en/tv.action \\
    {[Accessed:21-May-2019]}. \\

\item  BusinessWire. (2017) Elbit systems, general dynamics corporation, honeywell, leonardo - research and markets. \\
Available: {[Online]}.Available:https://www.businesswire.com/news/home/20170901005591/en/\\
Search-Rescue-SAR-Equipment-Market---Forecast.{[Accessed:14-Jun-2019]} \\

\item  Reuters. (2018) Indoor location market 2018 global trends, market share, industry size, growth, \\
opportunities and forecast to 2023. {[Online]}. Available: {[Online]}.\\
https: //www.reuters.com/brandfeatures/venture-capital/article?id=50849.{[Accessed:14-Jun-2019]}\\

\item A. Hayes, “Break-Even Analysis,” Investopedia, 31-Oct-2019. {[Online]}. \\
Available: https://www.investopedia.com/terms/b/breakevenanalysis.asp. {[Accessed: 11-Nov-2019]}.\\

\item CFI, "Break Even Analysis - Learn How to Calculate the Break Even Point", Break Even Analysis, 2019.\\
{[Online]}. Available: \\
https://corporatefinanceinstitute.com/resources/knowledge/modeling/break-even-analysis/. \\
{[Accessed: 11- Nov- 2019]}.\\

\item Digikey, "DWM1000 Decawave Limited | RF/IF and RFID | DigiKey", Digikey.com, 2019. 
{[Online]}. Available: https://www.digikey.com/product-detail/en/decawave-limited/DWM1000/1479-1002-2-ND/4805334. \\
{[Accessed: 11- Nov- 2019]}.

\item sparkfun, "Arduino Pro Mini 328 - 3.3V/8MHz - DEV-11114 - SparkFun Electronics", Sparkfun.com, 2019. \\
{[Online]}. Available: https://www.sparkfun.com/products/11114. {[Accessed: 11- Nov- 2019]}.\\

\item Amazon, "uxcell Double Sided Universal Printed Circuit Board for DIY Soldering 5pcs", Amazon.com, 2019. {[Online]}. \\
Available: https://www.amazon.com/uxcell-Universal-Printed-Circuit-Soldering/dp/B07FK3GFHS. \\
{[Accessed: 11- Nov- 2019]}.\\

\item Bittele Electronics, "Turn-key PCB Assembly", 7pcb.ca, 2019. \\
{[Online]}. Available: https://www.7pcb.ca/. {[Accessed: 11- Nov- 2019]}.\\

\item 3dhubs, "3D Hubs | On-demand Manufacturing: Quotes in Seconds, Parts in Days", 3D Hubs, 2019. \\
{[Online]}. Available: https://www.3dhubs.com/. {[Accessed: 11- Nov- 2019]}.\\


\end{enumerate}