
\
\section*{Abstract}	%For left alignment of title

\bigskip
The Akriveia Beacon by TRIWAVE SYSTEMS focuses on improving the locating and rescue process of personnel trapped in buildings during or after small scale disasters such as fires and low magnitude earthquakes. The Akriveia Beacon system allows search and rescue operations to safely and reliably locate trapped victims during and after a disaster situation within complex urban environments. By pinpointing the exact location of any victim wearing an ID tag, the search and rescue time for first responders is minimized; which is crucial in any disaster rescue operations.

\bigskip
The Akriveia Beacon consists of hardware, electrical and software components in order to accurately and reliably to locate and identify ID tags within a complex commercial building structure in near real time. This is achieved by incorporating a combination of advanced Ultra wideband radio modules, microcontroller units, data processing units, and reliable trilateration techniques to create a dependable indoor location positioning system. 

\bigskip
The design specifications outlined in this document detail the specifics of the design elements such as the high-level system architecture, functionality, and implementation for each critical section of the Akriveia Beacon. Such sections include details for the Systems, Hardware, Electrical, and Software components of the product. The specifications detailed will also cover the three phases of product development: Proof-of-concept (PoC) phase, Prototype phase, and Final Product phase. Additional appendices for the user interface design and 440 development plan are included at the end of this document. These appendices outlines the intended development timeline and task assignment breakdown for the development of the Akriveia Beacon.

\bigskip
TRIWAVE SYSTEMS is dedicated to creating a reliable and robust system design to improve disaster search and rescue operations with human safety as the pivotal focus.
