\setcounter{section}{3}
\section{Budget \& Funding}
\bigskip

\subsection{Expense Forecasting}
\medskip
In the following tables, expense that has already been put into the project, and the estimated costs for the remainder of the project are outlined.  The expenses are divided into two tables, one containing the expenses already incurred up to the time of this writing, and the other contains a forecast of the expected costs to come.

\begin{table}[H]
\centering
\begin{tabular}{ | m{4.75cm} | m{5cm} | m{2.5cm} | m{3cm} |}
\hline
\textbf{Item} & \textbf{Purpose} & \textbf{Cost [CAD]} & \textbf{Project Phase}  \\
\hline
12 of: nrf24l01 2.4GHz RF Transceiver modules & Initial feasibility testing & \$17.99 & PoC \\
\hline
5 of: ESP32 development boards & PoC and prototype testing and development & \$82.15 & PoC, Prototype, Final \\
\hline
1 of: Raspberry Pi 3 B+ starter kit & Will act as the demo central data processing unit for prototype and final product & \$88.47 & Prototype, Final \\
\hline
5 of: Decawave DWM1000 UWB modules & RF transceiver for Prototype and final product & \$230.67 & Prototype, Final \\
\hline
12 of: DWM1000 PCB breakout boards & Allow for DWM1000 modules to be used with ESP32 in prototype and final product & \$18.29 & Prototype, Final \\
\hline
Raspberry Pi 3 B+ & Will act as the central data processing unit for prototype and final product & \$88.47 & Prototype, Final \\
\hline
SMD components and solder paste & Assembling the DWM1000 boards & \$63.45 & Prototype, Final\\
\hline
Arduino boards and components & Testing and development for Data processing unit and serial communication & \$107.87 & PoC \\
\hline
\end{tabular}
\caption{Expenses to Date}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{ | m{3.5cm} | m{6.25cm} | m{2.5cm} | m{3cm} |}
\hline
\textbf{Item} & \textbf{Purpose} & \textbf{Cost [CAD]} & \textbf{Project Phase}  \\
\hline
3D printing & Casing for beacons and ID tags & \$50.00 & Final  \\
\hline
Batteries & Power supplies for system components & \$30.00 & Prototype, Final \\
\hline
Circuit components & Beacon and ID tag components & \$20.00 & Final \\
\hline
PCB printing & Beacon and ID tag components & \$20.00 & Final \\
\hline
\end{tabular}
\caption{Forecast of future expenses}
\end{table}

\pagebreak

\subsection{Prospective Funding Sources}
\subsubsection{Engineering Science Student Endowment Fund}
We hope to obtain funding from the SFU Engineering Science Student Society (ESSS) by means of the endowment fund set up by the society (ESSEF). We know that they have been very generous with Capstone groups in the past, so as soon as we are able to, we will be applying for funding from the ESSEF. We acknowledge that some parts purchased with the money from this source may have to be donated to the ESSS for their parts library.

\subsubsection{Wighton Development Fund}
The Wighton Development Fund is in place to support SFU student-led projects, awarded by Dr. Andrew Rawicz \cite{R4-1}, and a comitee consisting of other facuty or staff. We hope to obtain funding that will cover the remainder of the expenses endured during this project. As with the ESSEF, an application will be submitted by this group as soon as possible.

\subsubsection{Team Contributions}
If the above funding sources are insufficient to cover the costs of this project, each team member will agree to personal contributions up to \$50 each to complete funding for the project and cover any remaining expenses.




