\
\setcounter{section}{5}
\section{Company Details}

\bigskip
\textbf{Name}: Jerry Liu \\
\medskip
\textbf{Title}: Chief Executive Officer (CEO) \\
\medskip
\textbf{Background}: Jerry is a 5th year Computer Engineering student at Simon Fraser University where he has gained fundamental knowledge in programming, embedded systems, and  software development. From his previous experiences, he developed skills and comprehensive knowledge about hardware, software, and system level design. Jerry has co-op experience in the telecommunication industry from working at Sierra Wireless. At Sierra Wireless, he worked on industry leading, dual-LTE-Advanced vehicle networking platforms designed for applications in extremely harsh indoor, vehicle or exposed outdoor locations. He has also worked for two semesters as a co-op student under a professional research laboratory the Laboratory of Alternative Energy Conversion (LAEC). At LAEC he provided development for custom data analysis software in both MATLAB and python as well as built and maintained various experimental test beds for thermodynamics and heat transfer applications.

\bigskip
\bigskip
\textbf{Name} Jeffery Yeung \\
\medskip
\textbf{Title}: Chief Communications Officer (CCO)\\
\medskip
\textbf{Background}:
Jeffery is a sixth year engineering science student at SFU pursuing a degree in Systems Engineering. His previous experience includes 
working at Mix Technology Inc. in Hong Kong and Integral Group in the Vancouver office. He has gained valuable experience in PLC software
design and gained valuable insight into Hong Kong's diverse and booming construction industry. His time at Integral Group further cemented
his understanding of building verification and the importance of proper building commissioning. He hopes to apply his acquired skills and experience
in the construction industry towards machine learning for building HVAC. His goal is to reduce building HVAC energy consumption and 
advance sustainability or green practices in building design.

\bigskip
\bigskip
\textbf{Name}:  Keith Leung\\
\medskip
\textbf{Title}: Chief Technology Officer (CTO) \\
\medskip
\textbf{Background}:
Keith is a sixth year engineering science student pursuing a degree in computer engineering at Simon Fraser University. Through his academics, he has gained extensive software development experience with C and C++, as well as basic data mining knowledge with R. His past co-op experience at TELUS as a Wireless Access Engineer has exposed him to the telecommunication industry. At TELUS for three semesters, he performed extensive research and development on various wireless technology, including LTE, 3G, Wi-Fi and small cell indoor solution in lab environments. Keith specializes on an LTE-Advanced feature called Carrier Aggregation (CA) to establish throughput breakthroughs for commercial subscribers. As the CTO of Triwave Systems, he aims to be the solution architect to the wireless aspects involved with the project.

\pagebreak
\textbf{Name}: Scott Checko\\
\medskip
\textbf{Title}: Chief Operating Officer (COO)\\
\medskip
\textbf{Background}:
Scott is a 5th year Computer Engineering student at Simon Fraser Universtiy with a focus on development of webservers and embedded programming.
In his previous experience at SpeedLine he worked on a Cloud based MicroServer Platform for a new Online Ordering framework using Amazon Web Services that would serve restaurants across Northern America.
He also worked at Avigilon, maintaining and adding features for a physical Access Control application to manage Mercury and HID controllers and other hardware to prevent unauthorized user access into buildings.
At both SpeedLine and Avigilon, Scott learned to hone skills such as Agile workflow, collaberation software, teamwork, leadership, quality assurance, and a plethora of different programming languages ranging from C++ to Javascript, including the Yocto Project to build and maintain a custom Linux based operating system.

\bigskip
\bigskip
\textbf{Name}: Ryne Waterson\\
\medskip
\textbf{Title}: Chief Information Officer (CIO)\\
\medskip
\textbf{Background}: Ryne is a 6th year electronics engineering student at Simon Fraser University. His time in the program has given him skills in designing and analyzing electrical circuits, programming, and microelectronic systems. A minor in physics has allowed him to gain insight into the fundamental mechanics of natural systems. Ryne has experience working in research for Dr. Marinko Sarunic, doing all three semesters of co-op in his lab. During his time here, Ryne worked with cutting edge medical imaging systems, using Optical Coherence Tomography (OCT) to image mouse retina . At the end of his last term of co-op, Ryne attended the annual Association for Research in Vision and Ophthalmology (ARVO) research conference, where he presented his research alongside other research scientists from all over the world.  

