

\setcounter{section}{6}
\section{Conclusion}
\bigskip
As urban centers around the world experience rapid growth and changes so does the risk of being potentially trapped within buildings during disasters. The time period right after a disaster strikes is the most critical time for saving victims lives. In current practices, first responders have limited time to evaluate the situations when they arrive on the scene of disaster and must take crucial actions accordingly. Searching the incident building for possible victims is one of the major tasks undertaken by first responders after an incident occurs. The lack of timely information could be the difference between life and death in such situations.

\bigskip
As such, a reliable and accurate indoor location rescue system is needed to aid first responders in locating trapped personnel. The Akriveia Beacon is a system of anchor beacons and ID tags controlled by ESP32 micro-controllers and communicating via Decowave DWM1000 UWB modules, along with trilateration algorithm to accurately obtain near real time location of trapped personnel within buildings during the event of a disaster. The location data is then reported to a portable data processing unit via a closed WiFi network, which can be interacted with directly by emergency first responders and operators to provide accurate and reliable information for the search and rescue effort. 

\bigskip
This project proposal document provides a brief overview of the system architecture, a perspective on current markets and potential competitions, discuss project planning, available budget, and funding, as well as an introduction to the development team at TRIWAVE SYSTEMS. This proposal document will cover the mentioned section over the development of the Akriveia Beacon product through three different phases including: the proof-of-concept (completed August 2019), prototype, and final product (completed December 2019).

\bigskip
Although this project might be challenging, the team at TRIWAVE SYSTEMS is confident that through hard work and careful planning the Akriveia Beacon system will deliver all of its promised features. Even with a lack of external funding, the team is assured that the project will still meet its promised milestones and provide top end quality through a self-funded budget. As a product that could potentially affect the outcome of disaster relief operations, the Akriveia Beacon is designed with the utmost care. As aforementioned, TRIWAVE SYSTEMS is dedicated to creating a reliable and robust indoor location tracking system designed to improve disaster search and rescue operations with human safety as the pivotal focus.



