

\setcounter{section}{6}
\section{Conclusion}

\bigskip
As urban centers around the world experience rapid growth and changes so does the risk of being potentially trapped within buildings during disasters. The time period right after a disaster strikes is the most critical time for saving victims lives. In current practices, first responders have limited time to evaluate the situations when they arrive on scene of disaster and must take crucial actions accordingly. Searching the incident building for possible victims is one of the major tasks undertaken by first responders after an incident occurs. The lack of timely information could be the difference between life and death in such situations.

\bigskip
As such, an reliable and accurate indoor location rescue system is needed to aid first responders in locating trapped personnels. The Akriveia Beacon is a system of anchor beacons and ID tags controlled by ESP32 micro-controllers and communicating via Decowave DWM1000 UWB modules, along with trilateration algorithm to accurately obtain near real time location of trapped personnels within buildings during the event of a disaster. The location data is then reported to a portable data processing unit via a closed WiFi network, which can be interact with directly by emergency first responders and operators to provide accurate and reliable information for the search and rescue effort. 

\bigskip
The system overview, design, and constraints of the Akriveia Beacon system are clearly established in this document, as well as presenting the complete system design specifications. By provided a detailed outline of the design specifications this document is intended to be used as a design reference for the engineers at TRIWAVE SYSTEMS, as well as to provide detailed insight for the hardware and software designs required for the Akriveia Beacon product. These design specification outlines high level system architectures, system functions and implementation of the Akriveia Beacon product through three different phases of development including: the proof-of-concept (completed August 2019), prototype, and final product (completed December 2019).

\bigskip
As a product that could potentially affect the outcome of disaster relief operations, the Akriveia Beacon is designed with the utmost care. As aforementioned, TRIWAVE SYSTEMS is dedicated to creating a reliable and robust system design to improve disaster search and rescue operations with human safety as the pivotal focus.
