

\subsection{Engineering Standards}
\bigskip
To create an intuitive user interface for optimal user experience, the team at TRIWAVE SYSTEMS will be following several Engineering Standards throughout the development of for the Akriveia Beacon system user interface. The proposed user interface features two branch of components, hardware and software. The hardware components comprising of electronic components such as UWB radio modules and micro-controllers for the device. The software components is split up between data collection from the hardware and data processing. The software also serves as a point of communication and control for the user. The two branches should always inform the user of system operations with easy to understand and highly visible status displayed through the user interface. Interface should also designed in a way that potential errors are kept to a minimum.

\bigskip
These engineering standards published by the \Gls{IEEE}, the \Gls{IEC}, the \Gls{ISO}, and the \Gls{CSA} Group will ensure an intuitive, safe and reliable user interface. Note that some of the standards pertain to the user interface while others pertain to general safety guidelines. The Akriveia Beacon UI design will be built by and tested against the engineering standards listed in the following table.
\bigskip

\def\arraystretch{1.5}
\begin{table}[H]
\centering
\begin{tabular}{ | p{3.5cm} | p{11.5cm}| } 
\hline
\rowcolor{lightgray} \multicolumn{1}{|r|}{\textbf{Standard Code}} & \textbf{Description}\\ 
\hline
\multicolumn{1}{|r|}{CSA-C22.2 NO.61508-1:17} & Functional safety of electrical/electronic/programmableelectronic safety-related systems - Part 1: General requirements \cite{R10-5-1}\\ 
\hline
\multicolumn{1}{|r|}{IEEE 1621-2004} & User Interface Elements in Power Control of Electronic Devices Employed in Office/Consumer Environments \cite{R10-5-2}\\ 
\hline
\multicolumn{1}{|r|}{IEC TR 61997} & Guidelines for the user interface and accompanying word choices \cite{R10-5-3} \\ 
\hline
\multicolumn{1}{|r|}{ISO 20282} & Ease of operation for everyday products \cite{R10-5-4} \\ 
\hline
\multicolumn{1}{|r|}{IEC TR 61997} & Guidelines for the User Interface in Multimedia Equipment for General Purpose Use \cite{R10-5-5} \\ 
\hline
\multicolumn{1}{|r|}{IEEE P360} & Standard for wearable consumer electronic devices \cite{R10-5-6}\\ 
\hline
\multicolumn{1}{|r|}{C22.2 NO.0.23-15} & General Requirements for Battery-Powered Appliances \cite{R10-5-7}\\ 
\hline
\multicolumn{1}{|r|}{IEC 60417} & Graphical symbols for use on equipment \cite{R10-5-8}\\ 
\hline
\multicolumn{1}{|r|}{IEC 62366-1} & Guidance on Usability engineering for software \cite{R10-5-9}\\ 
\hline
\multicolumn{1}{|r|}{ISO/IEC 26907:2009} & Information technology -- Telecommunications and information exchange between systems -- High-rate ultra-wideband PHY and MAC standard \cite{R10-5-10} \\
\hline
\multicolumn{1}{|r|}{ISO/IEC 24730-62:2013} & Information technology -- Real time locating systems (RTLS) -- Part 62: High rate pulse repetition frequency Ultra Wide Band (UWB) air interface \cite{R10-5-11}\\ 
\hline
\end{tabular}
\caption{Engineering Standards}
\end{table}	









