

\subsection{Conclusion}
\medskip
The User Interface design for the proof-of-concept, prototype, and the final product of the Akrieva Beacon system developed by TRIWAVE SYSTEMS is detailed in the appendix. Currently the conceptual framework of the Akriveia Beacon system is under development, with the primary circuitry and initial interfaces under design and early implementations. The major feature to be implemented is the wireless communication interfaces and protocols between anchor beacons and ID tags; The control and data processing unit are also in parallel development. The final project goal is to showcase the Akriveia as an accurate, reliable, modular, and simple solution in providing automated indoor location tracking with near real time and multi-tracking capabilities.  

\bigskip
This appendix outlines a study of the user analysis, and technical analysis for interaction between the system and its intended users. As well as an overview of engineering safety and standards to ensure that the Akriveia Beacon system is safe and reliable for its designated users. Analytical usability testing and empirical usability testing will be performed to ensure that the basic system functionality, aesthetics, stability, and reliability are completely sufficient with of all planned requirements satisfied. 

\bigskip
With the help of this device under the intended scenario, primary users of the system such as firefighters and first responders will be able to locate trapped personnel with minimized search time; therefore, lowering rescue time and allowing for higher survival rate for trapped victims during the event of disasters. 













