

\setcounter{section}{6}
\section{Conclusion}
\bigskip

As urban centers around the world experience rapid growth and changes, so does the risk of being potentially trapped within buildings during disasters. The time period right after a disaster strikes is the most critical for saving victims. As such, a reliable and accurate indoor location rescue system is needed to aid first responders in locating trapped personnel. The Akriveia Beacon is a system of anchor beacons and ID tags designed to provide safe and reliable location information to first and rescue operations during such situations. 

\bigskip
As a system to be used during emergency disaster situations, it is critical that each of the component and the system as a whole must be designed in such a way where potential risks and failures are minimized or eliminated. To validate designs and to identify potential issues, a comprehensive test plan was made to ensure all major system components are functional and adhere to design requirements, standards and regulations. 

\bigskip
This detailed test plan was clearly outlined in this document to present the steps and processes in which the team will use as a reference to validate the Akriveia Beacon system. All major hardware, software, and electrical component of the Akriveia Beacon will be tested individually as well as integrated together as a system. Furthermore, to guarantee ease of use for the end users, a usability test plan is also provided. This test plan will ensure that the final Akriveia Beacon product will provide quality and assurance for its users.
